\section{Parabolic Equations}

For parabolic equations the maximum principle as well as its Corollary 1,
and the Hopf boundary lemma (see \cite{protter_maximum_1984}, Chapter 3, \S 3) hold.
Therefore all our results admit extensions to such equations with essentially the same proofs.
We shall content ourselves with the statement of several results for functions $u(t, x)$ 
defined in a cylinder $\Omega = (0 < t < T) \times G$, $G$ is a bounded domain in $\mathbb{R}^n$ 
with $\partial G$ smooth. 
By a (maximal) cap of f2 we always mean $[0 < t < T) \times [\text{a (maximal) cap of }G]$.

\noindent
\textit{Condition I. }With $G=R^{\prime}< |x| <R$, let $u$ be a positive solution of
\begin{equation}\label{eq:5.1}
	-u_t+\Delta u+f(t,r,u)=O, \qquad u=0 \quad \text{on}\quad |x|=R
\end{equation}
with $u_t$, $u_j$, $u_{kl}$ belonging to $C$ in the closure. Here $f$ and $f_u$ are continuous in $\bar{G}\times\mathbb{R}^+$. Assume that $f$ is decreasing in $r$ and that $u(0, x)$, is rotationally symmetric and decreasing in $r$.
\begin{theorem}\label{thm:5.1}
	Assume Condition I. Then
	\[u_r<0\quad \text{for}\quad \frac{R+R^{\prime}}{2} \leqq r <R.\]
	If, in addition, $u$ is a solution in $|x| <R$, then $\forall t, 0<t<T$, $u$ is radially symmetric and $u_r<O$ for $0<r<R$.
\end{theorem}

The next result extends Theorem \ref{thm:2.1prime} in which we consider a maximal cap $\Omega\cap\{x_1 > \lambda_1 \}$.\\

\noindent
\textit{Condition II. }Consider a positive solution in $G$ of
\[-u_t+F(t,x,u, u_i, u_{jk})=O,\qquad u=0 \quad\text{on}\quad \partial G\]
with $F$ as in Section 2.4 satisfying in particular condition (c), and assume $u(0, x)$ satisfies condition \eqref{eq:2.2}.
\begin{theorem}\label{thm:5.2}
	Assume Condition II. Then $\forall t$ in $0<t<T$, $u(t,x)$ satisfies condition \eqref{eq:2.2}. Furthermore if $u_1=0$ at some point $(x, t_0)$ in $\Omega\cap\{x_1=\lambda_1\}$ then for $0<t\leqq t_0$, $u$ is symmetric about the plane $x_1 =\lambda_1$ and \eqref{eq:2.3} holds.
\end{theorem}

The results in Sect.~3 also admit extensions to parabolic equations.